---
title: "Gait Analyzer"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    #social: menu
    #source_code: embed 
    theme: united
runtime: shiny
---

```{r setup, echo = FALSE, warning = FALSE, include = FALSE}
library(shiny)
library(reticulate)
library(tidyverse)
library(plotly)
py_install("pandas")
py_install("scikit-learn")
py_install("glob2")
```

```{r global, echo = FALSE, warning = FALSE, include = FALSE}
#read and evaluate python script to obtain model's prediction stats
source_python("get_model_stats.py")
overall = get_model_stats()
train_acc = overall[[1]]
test_acc = overall[[2]]
ideal_rand = overall[[3]]
true_ind = overall[[4]]
```

Inputs {.sidebar}
-----------------------------------------------------------------------

```{r}
# user can select a file from either the given gait_data folder of given data, or their own data
 fileInput("file", label = h4("Please select a text file from the gait_data directory"))
# there are 12 different waveform features that the user can view per file, here they select which one they are interested in viewing 
 radioButtons("waveform", label = h4("Select which waveform data to view"), 
                  choices = list("Left Stride Interval" = "lstride", "Right Stride Interval" 
                                 = "rstride", "Left Swing Interval" = "lswing", "Right Swing
                                 Interval" = "rswing", "Left Swing Interval (%)" = "lswing_int",
                                 "Right Swing Interval (%)" = "rswing_int", "Left Stance
                                 Interval" = "lstance", "Right Stance Interval" = "rstance",
                                 "Left Stance Interval (%)" = "lstance_int", "Right Stance 
                                 Interval (%)" = "rstance_int", "Double Support Interval" = 
                                 "dsupport", "Double Support Interval (%)" = "dsupport_int"), 
                  selected = "lstride")
```

Row {data-height=700, .tabset}
-----------------------------------------------------------------------

### Raw Data

```{r}
#plotting the raw form of the waveform data chosen by the user for a selected gait time series data file
uiOutput("dynamic")
#created function for using the name of selected file to read in file's data
FileDF = function(filename) {
  file = read.table(paste0("gait_data/",filename$name))
  keys = c('time', 'lstride', 'rstride', 'lswing', 'rswing', 'lswing_int', 'rswing_int',
            'lstance', 'rstance', 'lstance_int', 'rstance_int', 'dsupport', 'dsupport_int')
  colnames(file) = keys
  return(file)
}
#make sure file is one of the txt data files 
output$dynamic <- renderUI({
  if (!is.null(input$file)) {
    filename = input$file
    if (str_detect(filename$name, ".txt")) {
      if ((str_detect(filename$name,"als")) || (str_detect(filename$name, "park")) ||
        (str_detect(filename$name, "hunt")) || (str_detect(filename$name, "control")) ||
        (str_detect(filename$name, "test"))) {
          plotlyOutput("plot")
        } else textOutput("invalidtxt")
      }
    else textOutput("invalidtxt")
  }
  else textOutput("text")
})
#plot the raw data
output$plot <- renderPlotly({
  
                  p = ggplot(FileDF(input$file), aes_string(x = "time", y = input$waveform)) + xlab("Time (sec)") + geom_line()
                  print(p)
                })
output$text <- renderText({ "No file selected" })
output$invalidtxt <- renderText({"Invalid file selected"})

```

### Processed Data

```{r}
# plotting the processed form of the waveform data chosen by the user for a selected gait time series data file
uiOutput("dynamic2")
#created a function for data pre-processing 
ProcessDF = function(filename) {
  #read in data from the file selected by the user
  file = read.table(paste0("gait_data/",filename$name))
  keys = c('time', 'lstride', 'rstride', 'lswing', 'rswing', 'lswing_int', 'rswing_int',
            'lstance', 'rstance', 'lstance_int', 'rstance_int', 'dsupport', 'dsupport_int')
  colnames(file) = keys
  processed = file
  
  #create a column with normalized time, starting from 0
  normTime = 0
  time1 = as.numeric(unlist(processed$time))
  for (i in seq(1, length(time1)-1)) {
    normTime = append(normTime, time1[i]-time1[1])
  } 
  processed$normTime = normTime
  #use mean imputation to replace outlier points in the waveform
  for (key in keys) {
        temp = as.numeric(unlist(processed[key]))
        z = abs(temp - mean(temp))/sd(temp)
        ind = which(z > 3)
        temp[ind] = mean(temp)
        processed[key] = temp
  }
  processed <- processed %>% select(-'time')
  return(processed)
}
#make sure file is one of the txt data files
output$dynamic2 <- renderUI({
  if (!is.null(input$file)) {
    filename = input$file
    if (str_detect(filename$name, ".txt")) {
      if ((str_detect(filename$name,"als")) || (str_detect(filename$name, "park")) ||
        (str_detect(filename$name, "hunt")) || (str_detect(filename$name, "control")) ||
        (str_detect(filename$name, "test"))) {
          plotlyOutput("plot2")
        } else textOutput("invalidtxt2")
      }
    else textOutput("invalidtxt2")
  }
  else textOutput("text2")
})
#plot processed data, also plotted vertical lines to symbolize where statistical features were calculated for each 30 second time zone. 
output$plot2 <- renderPlotly({
                  p = ggplot(ProcessDF(input$file), aes_string(x = "normTime", y = input$waveform)) + xlab("Normalized Time (sec)") + geom_line() + geom_vline(xintercept =  c(0, 30, 60, 90, 120, 150, 180, 210, 240, 270, 300), color = "blue", linetype = "dashed")
                  print(p)
                })
output$text2 <- renderText({ "No file selected" })
output$invalidtxt2 <- renderText({"Invalid file selected"})

```

### Final Prediction

Note: The prediction shown is based off the entire file, not just the selected component.

```{r}

uiOutput("final")
#read and evaluate python script to obtain model's prediction for the uploaded data
getPred = function(filename) {
  file = filename$name
  source_python("get_model_pred.py")
  prediction = get_model_pred(file, true_ind)
  return(prediction)
}

output$final <- renderUI({
  if (!is.null(input$file)) {
    filename = input$file
    if (str_detect(filename$name, ".txt")) {
      if ((str_detect(filename$name,"als")) || (str_detect(filename$name, "park")) ||
        (str_detect(filename$name, "hunt")) || (str_detect(filename$name, "control")) ||
        (str_detect(filename$name, "test"))) {
          textOutput("predtxt")
        } else textOutput("invalidtext")
      }
    else textOutput("invalidtext")
  }
  else textOutput("txt")
})
#print prediction for user
output$predtxt <- renderText({paste("Based on this file, we predict that
                                    the subject",getPred(input$file))})
output$txt <- renderText({ "No file selected" })
output$invalidtext <- renderText({"Invalid file selected"})

```

Row {data-height=300, .tabset}
-----------------------------------------------------------------------

### About

Welcome to the Gait Analyzer tool! Here, we look at gait readings from force-sensitive resistors to determine whether a person has ALS, Parkinson's, Huntington's, or none of the above. 

We have trained a Random Forest model to make predictions. The train accuracy of the model is: `r train_acc` and the test accuracy of the model is: `r test_acc`. 

To learn more about the dataset we used, visit https://www.physionet.org/content/gaitndd/1.0.0/ 

### Instructions

You can select one of the provided text files (in the gait_data directory) to see how we process the data and make predictions. If you want to upload your own data, please make sure the format is the same as the examples provided. In order for this tool to work, you *must* have your data in the .txt file format, and the file itself has to be *in the gait_data directory*. Also make sure the file you provide includes "test" in the name. 

**Important**: Please see the information under "Disclaimer" *before* uploading your own data. 

### Disclaimer

This tool was created for a class and HAS NOT been scientifically validated. Any results derived from this app should be taken with a grain of salt. We are not doctors. This app is not meant to provide any definitive diagnoses. If you have any concerns relating to your gait, please consult a professional instead of relying on what this app says. 

Furthermore, the model we are using has been trained and tested on a very small number of samples (48 and 16, respectively). Therefore, the accuracy provided may not be representative of how our model would perform in a real-world setting. 
