---
title: "Gait Analyzer"
output: 
  flexdashboard::flex_dashboard:
    social: menu
    source_code: embed 
runtime: shiny
---

```{r setup, echo = FALSE, warning = FALSE, include = FALSE}
library(shiny)
library(reticulate)
library(tidyverse)
library(plotly)
py_install("pandas")
py_install("scikit-learn")
py_install("glob2")
```

```{r, echo = FALSE, warning = FALSE, include = FALSE}
source_python("get_model_stats.py")
overall = get_model_stats()
train_acc = overall[[1]]
test_acc = overall[[2]]
ideal_rand = overall[[3]]
train_data = overall[[4]]
train_labels = overall[[5]]
```

## About

The train accuracy of the model is: `r train_acc` and the test accuracy of the model is: `r test_acc`.

### Disclaimer

This tool was created for a class and HAS NOT been scientifically validated. Any results derived from this app should be taken with a grain of salt. We are not doctors. This app is not meant to provide any definitive diagnoses. If you have any concerns relating to your gait, please consult a professional instead of relying on what this app says. 

Furthermore, the model we are using has been trained and tested on a very small number of samples (51 and 14, respectively). Therefore, the accuracy provided may not be representative of how our model would perform in a real-world setting. 