---
title: "Gait Analyzer"
output: 
  flexdashboard::flex_dashboard:
    social: menu
    source_code: embed 
runtime: shiny
---

```{r setup, echo = FALSE, warning = FALSE, include = FALSE}
library(shiny)
library(reticulate)
library(tidyverse)
library(plotly)


library(flexdashboard)
library(magrittr)
library(dplyr)
library(devtools)
library(ggplot2)
library(reshape2)
library(tidyr)
library(leaflet)
#py_install("pandas")
#py_install("scikit-learn")
#py_install("glob2")
```

```{python, include=FALSE}
import pandas as pd
import numpy as np
import glob
keys = ['time', 'lstride', 'rstride', 'lswing', 'rswing', 'lswing_int', 'rswing_int', 'lstance', 
        'rstance', 'lstance_int', 'rstance_int', 'dsupport', 'dsupport_int']
        
files = glob.glob('gait_data/control*.{}'.format("txt"))
control = pd.DataFrame()
all_pat = np.array([9])
count = 1

for file in files:
    X = pd.read_table(file,header=None)
    control = pd.concat([control,X], ignore_index=True)
    patient = np.ones(len(X), dtype=int) * count
    all_pat = np.concatenate((all_pat, patient))
    count += 1

control.columns = keys
all_patients = np.delete(all_pat, 0)
control['patient'] = all_patients
control['combpatient'] = all_patients
control['label'] = 0

files = glob.glob('gait_data/als*.{}'.format("txt"))
als = pd.DataFrame()
all_pat = np.array([9])
count = 1

for file in files:
    X = pd.read_table(file,header=None)
    als = pd.concat([als,X], ignore_index=True)
    patient = np.ones(len(X), dtype=int) * count
    all_pat = np.concatenate((all_pat, patient))
    count += 1

als.columns = keys
all_patients = np.delete(all_pat, 0)
als['patient'] = all_patients
numpat_control = np.asarray(control.combpatient)
als['combpatient'] = all_patients + numpat_control[-1] 
als['label'] = 1

#huntingtons
files = glob.glob('gait_data/hunt*.{}'.format("txt"))
hunt = pd.DataFrame()
all_pat = np.array([9])
count = 1

for file in files:
    X = pd.read_table(file,header=None)
    hunt = pd.concat([hunt,X], ignore_index=True)
    patient = np.ones(len(X), dtype=int) * count
    all_pat = np.concatenate((all_pat, patient))
    count += 1

hunt.columns = keys
all_patients = np.delete(all_pat, 0)
hunt['patient'] = all_patients
numpat_als = np.asarray(als.combpatient)
hunt['combpatient'] = all_patients + numpat_als[-1] 
hunt['label'] = 2

#parkinsons
files = glob.glob('gait_data/park*.{}'.format("txt"))
park = pd.DataFrame()
all_pat = np.array([9])
count = 1

for file in files:
    X = pd.read_table(file, header = None)
    park = pd.concat([park, X], ignore_index=True)
    patient = np.ones(len(X), dtype=int) * count
    all_pat = np.concatenate((all_pat, patient))
    count += 1

park.columns = keys
all_patients = np.delete(all_pat, 0)
park['patient'] = all_patients
numpat_hunt = np.asarray(hunt.combpatient)
park['combpatient'] = all_patients + numpat_hunt[-1] 
park['label'] = 3

alldat = pd.concat([control, als, hunt, park])
#alldatz = alldat.sample(frac=1).reset_index(drop=True)

```

```{r}


alldat <- py$alldat
alldat
```

Inputs {.sidebar}
-----------------------------------------------------------------------
```{r}
selectInput("disease", 
            label = h4("Select a disease type from the gait_data directory"), 
            choices = list("Control" = 0, 
                           "Amyotrophic lateral sclerosis" = 1, 
                           "Huntingtons" = 2, 
                           "Parksinsons" = 3), 
            selected = 0)
    
selectInput("Patient number", 
            label = "Select patient number", 
            choices = 1:16)



observeEvent(input$disease,{
  pats <- alldat[alldat$label == input$disease,]$combpatient[1]:alldat[alldat$label == 0,]$combpatient[nrow(alldat[alldat$label == input$disease])]
  updateSelectInput(session,"Patient number",
                    choices = pats)
})

  


radioButtons("waveform", 
             label = h4("Select which waveform data to view"), 
             choices = list("Left Stride Interval" = "lstride", 
             "Right Stride Interval" = "rstride", 
             "Left Swing Interval" = "lswing", 
             "Right Swing Interval" = "rswing", 
             "Left Swing Interval (%)" = "lswing_int", 
             "Right Swing Interval (%)" = "rswing_int", 
             "Left Stance Interval" = "lstance", 
             "Right Stance Interval" = "rstance",
             "Left Stance Interval (%)" = "lstance_int", 
             "Right Stance Interval (%)" = "rstance_int", 
             "Double Support Interval" = "dsupport", 
             "Double Support Interval (%)" = "dsupport_int"), 
             selected = "lstride")

```


```{r}
uiOutput("dynamic")

ProcessDF = function(filename) {
  file = read.table(paste0("gait_data/",filename$name))
  keys = c('time', 'lstride', 'rstride', 'lswing', 'rswing', 'lswing_int', 'rswing_int',
            'lstance', 'rstance', 'lstance_int', 'rstance_int', 'dsupport', 'dsupport_int')
  colnames(file) = keys
  for (key in keys) {
        temp = np.asarray(file[key])
        z = np.abs(stats.zscore(temp))
        ind = np.where(z > 3)
        temp[ind] = np.mean(temp)
        file[key] = temp
  }
  return(file)
}

output$dynamic <- renderUI({
  if (!is.null(input$file)) {
    filename = input$file
    if (str_detect(filename$name, ".txt")) {
      if ((str_detect(filename$name,"als")) || (str_detect(filename$name, "park")) ||
        (str_detect(filename$name, "hunt")) || (str_detect(filename$name, "control")) ||
        (str_detect(filename$name, "test"))) {
          plotlyOutput("plot")
        } else textOutput("invalidtxt")
      }
    else textOutput("invalidtxt")
  }
  else textOutput("text")
})

output$plot <- renderPlotly({
                  p = ggplot(ProcessDF(input$file), aes_string(x = "time", y = input$waveform)) + geom_line()
                  print(p)
                })
output$text <- renderText({ "No file selected" })
output$invalidtxt <- renderText({"Invalid file selected"})
```



Row {data-height=400, .tabset}
-----------------------------------------------------------------------

### About

The train accuracy of the model is:  and the test accuracy of the model is: . 

For more information, visit https://www.physionet.org/content/gaitndd/1.0.0/ 

### Disclaimer

This tool was created for a class and HAS NOT been scientifically validated. Any results derived from this app should be taken with a grain of salt. We are not doctors. This app is not meant to provide any definitive diagnoses. If you have any concerns relating to your gait, please consult a professional instead of relying on what this app says. 

Furthermore, the model we are using has been trained and tested on a very small number of samples (51 and 14, respectively). Therefore, the accuracy provided may not be representative of how our model would perform in a real-world setting. 